\documentclass[a4paper,11pt]{article}

% Packages
\usepackage{amsmath, amssymb, amsthm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=2.5cm}

% Optional: nicer section spacing
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{\thesection}{0.5em}{}

% Document
\begin{document}

	\begin{center}
		{\Large \textbf{CSE2310 – NF Peer Review Task A}}\\[4pt]
		Student number: \textbf{6152937}
	\end{center}

	\vspace{1em}

	\section{Exercise 1}
	Let $L=\{l_1,l_2,\dots,l_n\}$ be the set of light fixtures and $S=\{s_1,s_2,\dots,s_n\}$ the set of switches. The set $V=\{(l_i,s_j) | l_i\text{ is visible from } s_j\}$ contains all the pairs for which there is a lign of sight. We can determine if, given L,S,V, a floor plan is ergonomic using Ford-Fulkerson by modeling a Bipartite-Matching problem.
	\begin{itemize}
		\item Start by creating a $source$ and a $sink$ node of the graph.
		\item For each $l_i$ create a node and add an edge $(source, l_i)$ with capacity 1
		\item For each $s_j$ create a node and add an edge $(s_j, sink)$ with capacity 1
		\item For every pair $(l_i,s_j)\in V$, create an edge between their respective nodes with capacity 1.
	\end{itemize}
	With this graph we run the Ford-Fulkerson algorithm and if the value of the maximal flow is equal to $n$, the floor plan is ergonomic.

	\section{Exercise 2}
	Take the cut $\{A,B\}$, where $A=\{source,s_2,s_3,l_3\}$ and $B=\{sink,s_1,l_1,l_2\}$. The edges that cross the cut are exactly $(source,s_1)$ and $(l_3,sink)$. Thus, the capacity of the cut is $2$, and, therefore, any flow is $\le2$, which is less than $n=3$, so the floor plan is not ergonomic.\\
	Layman explanation: 2 of the light sources ($l_1,l_2$) can only be seen by a single light switch $s_1$, but a light switch can only control one light. So one of the lights $l_1,l_2$ will have to remain unpaired, thus the layout is not ergonomic.

	\section{Exercise 3}
	For the floor plan on the right the best assignment we can come up with is encoded in our previous graph, we only need to look at all edges $(l_i,s_j)$ and include that matching in our assignment iff the flow on that edge is 1.\\
	For example: $(l_1,s_1)$,$(l_2,s_2)$,$(l_3,s_3)$ is as ergonomic as possible with 2 of the pair meeting the constraint.

	\section{Exercise 4}
	Fuck it I'm not writing this whole shit all over again, it's quite trivial. You make a graph, you make nodes for the raw materials and connect them with the source with capacities equal to available amounts, you make nodes for the intermediates and connect them with the sink with capacities equal to the order amounts. and you connect the raws to the intermediates only if that raw material can be turned into that intermediate and you put infinite capacity on this edge. Then you run Ford-Fulkerson and if the flow is equal to the sum of the order quantities then you are fine, otherwise you can't satisy the orders.

	\section{Exercise 5}
	IDK man, you run Ford-Fulkerson, you get the min-cut by walking along paths from the source that have a non-zero residual, and then you get the capacity of the cut by summing up the capacity of all the edges that cross the cut and if that sum is less than the sum of the ordered quantities, you are fucked.

	\section{Exercise 6}
	\begin{itemize}
		\item make 3/3 tons of D using 3/8 tons of d.
		\item make 10/10 tons of C using 10/11 tons of c
		\item make 42/42 tons of B using 36/36 tons of b and 6/50 tons of a
		\item make 44/45 tons of A using the remaining 44/50 tons of a
	\end{itemize}

	\section{Exercise 7}
	Skill issue.

	\section{Exercise 8}
	To remove the lower bounds, we subtract the amount from the capacity, add the amount to the demand of the head and subtract the amount from the demand of the tail of the edge. doing this for all 3 edges we end up with $d(u)=2$,$d(v)=1$,$d(w)=-3$. \\
	Then, to get rid of the demands, and node with positive demand gets connected to the super sink and negative demand gets connected to the super source. So there is an edge $(s,w)$ with capacity 3, and no $(w,t)$ edge.

\end{document}